\documentclass[a4paper,12pt,titlepage]{article}

% custom paragraph to have line break after using mbox to hack :-/
\newcommand{\myparagraph}[1]{\paragraph{#1}\mbox{}\\}

% import graphicx package so we can import images
\usepackage{graphicx}

% so we can use sidewaystable
% \usepackage[figuresleft]{rotating}

\begin{document}

\iffalse
Page 1: Title Page – including the title of the project, the name of the author, the
date, the word count and the statement specified below under report details.
\fi

\include{title}

\include{abstract}

\iffalse
Page 3: Table of Contents - including page numbers of each chapter heading and
each appendix.
\fi

\tableofcontents

\include{introduction}

\include{literature}

\include{method}

\include{system}

\include{testing}

\include{conclusion}

\include{review}

\include{references}

\end{document}
Chapter 3: Research/Development Method - the overall approach and rationale.
Why the project was tackled in the chosen way, and why other ways were ruled out.
Chapter 4: Data/Findings/Designs - the project outcome. This might be data
collected and tabulated or the design of a program, or whatever outcome was
obtained.
Chapter 5: Analysis/Evaluation/Testing – assessing or testing the project outcome.
If the project is of type 2 are the results plausible? If the project is of type 3 or 4 then
any computer code should be tested using a range of inputs.
Chapter 6: Conclusions/Recommendations - as a result of the project. The project
does not need to have a positive conclusion. For example, it might prove that some
system was not effective or successful. You should indicate to what extent your
objectives have been achieved.
Chapter 7: Review/Reflections - this is often missed out by students but is very
important. It is an opportunity to, firstly, review on a personal level what you have
achieved, how you achieved it, what took the most time, the problems faced, the way
in which they were overcome, etc. Secondly, it is an opportunity to reflect on the
project with the benefit of hindsight. What might have been done differently? Was the
research method adequate? How could the project have been more successful?
Examiners like to see evidence of learning and mature reflection
Chapter 8: References - all references should be cited in the body of the report. A
typical reference in the report might take the form, “Donar and Kebab (1996) suggest
that high cholesterol levels do not lead to heart disease\ldots.” or “empirical eating studies
show that\ldots. (Donar and Kebab, 1996)”. The full title of the article or book or web
page in which Donar and Kebab make these assertions is then given in the list of
references. Where possible, use an article or a book rather than a web page. The idea
of references is not just to substantiate statements and arguments but also to make it
possible for other people to find the references. Normally, for a book, you should list
author(s), title, publisher, date of publication, relevant page number(s). It can be
difficult to locate the relevant part of a book if the page numbers are omitted. For an
article list author(s), title of article, name of journal, volume and issue number, date,
and page numbers of the article. In the academic world references are regarded as
very important and poor referencing will certainly detract from the project report. Do
not under any circumstances quote from a source without making it clear that
you are quoting. Any quote must be accompanied by an appropriate reference.
Chapter 9: Bibliography - list any relevant literature that has not been cited in the
report. (It is not a very well-kept secret that examiners tend to think that anything in a
bibliography has not in fact been read by the student. Of course this is a monstrous
slur but nevertheless do not waste too much time on the bibliography. Concentrate on
the references!)
Chapter 10: Appendices - these are not obligatory. Only put in relevant items not
already in the body of the report. These might include a questionnaire used to gather
information, a list of the people interviewed and their companies, transcripts of
interviews, detailed data, program listings, test results, etc. Any appendix should be
referred to in the main part of the report and not just stuck at the end of the report
without explanation. It is very important that an examiner can find evidence for the
claims you make in your report. The appendices are the place to put such evidence
without cluttering up the main part of the report.

